
\documentclass[11pt,a4paper]{extarticle}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{arial}
\usepackage[swedish]{babel}
\usepackage{comment}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{float}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{authblk}
\usepackage{url}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage[margin=0.984in]{geometry}
\usepackage{placeins}         % Permets de vider le buffer de flottants avec \FloatBarrier
\usepackage{epstopdf}
\usepackage{pgfgantt}


\usepackage{color,framed}            % Utilisation des couleurs et de l'environnement shaded
\definecolor{shadecolor2}{rgb}{.92,.92,.92} % choix de la teinte de ``shaded''
\definecolor{shadecolor}{rgb}{.6,.95,.6} % choix de la teinte de ``shaded''
\usepackage[pagebackref=true,
            colorlinks=true,
            linkcolor=blue,
            anchorcolor=blue,
            citecolor=blue,
            filecolor=blue,
            menucolor=blue,
            urlcolor=blue,
            plainpages=true,
            pdfpagemode=UseThumbs,
            pdftitle={Titre},
            pdfauthor={ORDECSYS},
            pdfsubject={Sujet},
            pdfstartview=FitH]{hyperref} % Extensions PDF
\def\pdfBorderAttrs{/Border [0 0 0] } % Options PDF (No border around Links)
\renewcommand\Affilfont{\itshape\small}
\linespread{1.5}


\begin{document}
\textbf{CV Tommy Lundgren}\\*
\textbf{Higher education degree}\\*
1996, Umeå University, Economics.\\*
\textbf{Doctoral degree}\\*
2001, Swedish University of Agricultural Sciences, Economics, “Dynamic Factor Demands and Environmental Investments” (supervised by Bengt Kriström).\\*
\textbf{Post-doctoral positions}\\*
2002, University of Calgary (Canada), Department of Economics.\\*
2005, University of Otago (New Zealand), Department of Economics.\\*
\textbf{Docent level}\\*
2007, Umeå University, Department of Economics, Umeå School of Business and Economics.\\*
\textbf{Current positions}\\*
Main affiliation: Centre for Environmental and Resource Economics (CERE), a joint venture between Umeå University and Swedish University of Agricultural Sciences. (www.cere.se).\\*
1. Professor of Economics (guest), Umeå School of Business and Economics (USBE), Umeå University, Umeå, Sweden. 2012-07-01 - …  . Research 100%.\\*
2. Researcher, Department of Forest Economics, SLU, Umeå, Sweden. 2006-10-01 – … . Research 80\%.\\*
\textbf{Previous positions}\\*
1. Researcher, Department of Forest Economics, SLU, Umeå, Sweden 2001-06-09 – 2006-09-30. Research 80\%.\\*
2. Researcher (FoAss and Lektor), Umeå School of Business and Economics, Umeå University, 2006-10-01 – 2012-06-30. Research 100\%.\\*
\textbf{Supervision}\\*
Ph D’s:\\*
Örjan Furtenback, 2011.\\*
Shanshan Zhang, scheduled 2015.\\*
Mathilda Eriksson, scheduled 2014.\\*
Erik Brockwell, scheduled 2014.\\*
Post-doc’s:\\*
Jurate Jaraite, 2013.\\*
Andrius Kazukaukas, 2013.\\*
\textbf{Prizes and awards}\\*
Kungliga Skytteanska samfundet (the Royal Skytteanska Society) prize to promising young researcher in environmental economics, May 2004.\\*
The Globe Award (2008). Selected as winner of the Best CSR Research (corporate social responsibility research) “for an outstanding and tangible research in the field of CSR”. The prize was handed out by Her Royal Highness and Crown Princess Victoria Bernadotte.\\*
\textbf{Brief description of past and current projects}\\*
The determinants of investment in the Swedish forest industry, 1996-1998. Wallander/Hedelius fund, Handelsbanken. (with Bengt Kriström).\\*
Environmental investments – applications to the Swedish forest industry, 1998 - 2001. Principal investigator. Wallander/Hedelius fund, Handelsbanken. (with Bengt Kriström).\\*
Swedish timberland investments – assessment of investment performance, 2001 – 2002 (FORMAS). (with Peichen Gong).\\*
The MountainMistra project, 2003-2006. Principal investigator for one of three theoretical frameworks (measuring regional welfare), and also principal researcher in sub-project concerning economic trends and economic development, in the Swedish mountain area.\\*
Taxing waste incineration and the effects of a kilometer tax, 2005 – 2006. Principal investigator. The royal Swedish academy of agriculture and forestry, KSLA.\\*
Direct and indirect effects of environmental policy on the Swedish forest sector, 2006-2008 (FORMAS). Principal investigator (with Bengt Kriström).\\*
The significance of transport costs in Swedish Forest Industry, 2006 – 2007. Effects on factor demand in Swedish manufacturing of a kilometer tax on heavy vehicles. (Joint project with Magnus Sjöström and Henrik Hammar, National institute of economic research, KI).\\*
Sustainable Investment Research Platform (SIRP), 2006-2012. MISTRA financed. Umeå School of Business and Economics (USBE). Principal investigator on sub-project concerning research on corporate social responsibility and environmental performance in Swedish industry. (see www.sirp.se).\\*
Bioenergy, the Climate, and Economics, 2008-2012 (FORMAS). Principal investigator.\\*
The economics of biofuels and the effects on climate and welfare of societies. Impact of energy and environmental policy on sustainable development and competitiveness in Swedish industry, 2011-2013 (Energimyndigheten – the Swedish Energy agency). Principal investigator.\\*

\pagebreak
\textbf{CV Örjan Furtenback}\\*
\textbf{Higher education degree}\\*
1999, Master of Science: Computer Science, The Royal Institute of Technology Stockholm\\*
\textbf{Doctoral degree}\\*
2011, Department of Forest Economics, Swedish University of Agricultural Sciences Umeå, “Three Essays on Swedish Energy and Climate Policy Options -
Dynamic CGE-models with Heterogeneous Forests and an Econometric Model of Fuel
Substitution in District Heating Plants” (supervised by Bengt Kriström).\\*
\textbf{Post-doctoral positions}\\*
2013, Centre for Environmental and Resource Economics (CERE),  a joint venture between Umeå University and Swedish University of Agricultural Sciences. (www.cere.se).\\*
\textbf{Current positions}\\*
Post-doctoral at the Centre for Environmental and Resource Economics (CERE), research 100 \% 2013-10-01 -.\\*
\textbf{Previous positions}\\*
2012-2013, Researcher at the National Institute of Economic Research, Stockholm, Sweden.\\*
2003, Software consultant at Dotway AB, Malmö.\\*
2002-2003, Self-employed, Stockholm.\\*
1999-2002, Software development manager at SATISFACTORY AB, Stockholm.\\*
1998-1999, Software consultant at Guide Förädling AB, Stockholm.\\*
1997-1998, Software consultant at Resco AB, Stockholm.\\*
1996-1997, Research engineer at Karolinska Institutet, Department of Medical Laboratory Sciences and Technology, Huddinge.\\*

\pagebreak
\textbf{CV Santosh Ram Joshi}\\*
\textbf{Higher education degree}\\*
2005, Master of Science: Environmental Economics, Wageningen University, The Netherland\\*
\textbf{Degree of Doctor}\\*
2011, J.E. Cairnes School of Business and Economics, National University of Ireland Galway, Ireland, Function forms and AGE Models: Understanding the implication of trade liberalization for the Global Economy, supervised by Late Dr Eoghan Garvey, Eithne Murphy and Dr. Hugh Kelley.\\*
\textbf{Postdoctoral position}\\*
2011-2013, Economics and Environmental Management Laboratory, Ecole Polytechnic Federal de Lausanne (EPFL), Switzerland.\\*
\textbf{Present position}\\*
2014 – , Post-Doctoral Researcher, Research 100\%, Centre for Environmental and Resource Economics (CERE) and Umeå School of Business and Economics,Umeå University.\\*
\textbf{Previous position}\\*
2007-2009, Teaching Assistant, J.E. Cairnes School of Business and Economics, National University of Ireland Galway (NUIG), Ireland.\\*
Aug 2004 - Jan 2005, Research Assistant, Canadian Energy Research Institutes (CERI), Canada\\*
2002-2003, Research Assistant, International Union for Conservation of Nature (IUCN),Nepal\\*
\textbf{Other information that is relevant to your application}\\*
\textit{Short course}\\*
August 2007, Purdue University, West Lafayette, Indianapolis, USA on Global Trade Analysis.\\*
September 2010, ETH Zurich, Zurich,  Switzerland on Dynamic General Equilibrium Analysis.\\*
\textit{Scholarships and awards}\\*
TEAGASC Walsh Fellowship awarded by TEAGASC, Ireland to pursue Ph.D.\\*
Netherlands Fellowship Program awarded by Government of Netherlands to pursue Masters of Sciences.\\*
Colombo Plan Scholarship awarded by Government of India to pursue Bachelor of Engineering.\\*
\textit{Visiting Scholar}\\*
Department of Economics, University of California, Davis, USA\\*

\end{document}

