\input{preamble}
% Times New Roman with size 12pt recommended
\begin{document}

\title{Assessing nuclear phase out in Sweden from an energy and macroeconomic perspective}
\maketitle
\author{}
\date{}
\section{Summary}
Sweden has the ambition of showing the way to a sustainable society and energy agenda is at the forefront of political debate. There is a political consensus on the expansion of renewable energy, promotion of energy efficiency and non expansion of hydropower. Nonetheless, the main political conflict concerns the future of nuclear power. In addition, a restriction in the supply of nuclear power will have significant economic consequences in a country like Sweden with a large element of power-intensive industries dependent on a stable and affordable supply of electricity. Given the ambitious greenhouse gases(GHGs) emission reduction target, and the challenge of meeting the increasing demand of electricity, Swedish nuclear energy policy and electricity sector needs to be scrutinized further; the economic stakes are high. It is necessary to invest in this direction of research to better understand the economic consequences of such ambitious climate policies. The research project we are proposing here intends to analyze the socio-economic costs and effects of restrictions on nuclear power capacity in combination with an expansion of renewable (weather dependent or intermittent) power sources, in Swedish electricity production. A computable general equilibrium (CGE)model will be developed to analyze these issues from a economy-wide perspective. The tool developed in this project will be an important contribution to policy modeling effort for Swedish energy system in general and nuclear phase out in particular.

Sweden seeks to be a forerunner in climate policy and governmental reports stress the urgency of curbing anthropogenic atmospheric greenhouse gases (Roadmap for a fossil fuel independent transport system in 2030 \cite{SOU201384} and Sweden - an emissions-neutral country by 2050 \cite{sepa2012}). There is also political consensus on the expansion of renewable energy, promotion of energy efficiency and non expansion of hydropower. Nonetheless, the main political conflict regards the future of nuclear power. The green party wants a quick phase out, while e.g. the liberal party support replacement of existing reactors. A larger variability and increasing demand for electricity is expected \cite{sepa2012, SOU201384}. Given the ambitious GHGs emission reduction target \cite{SOU201384}, and the challenge of meeting the increasing demand of electricity, Swedish nuclear power policy and electricity sector needs to be scrutinized further; the economic stakes are considerable.


\section{Popular scientific description (in Swedish)}
Det råder parlamentarisk oenighet i frågan om kärnkraftens vara eller icke vara i den svenska energipolitiken. En begränsning i utbudet av kärnkraften kommer att få ekonomiska konsekvenser i ett land som Sverige med ett stort inslag av elintensiv industri som är beroende av en stabil elförsörjning. Det forskningsprojektet vi föreslår avser att analysera samhällsekonomiska konsekvenser och spridningseffekter av restriktioner på svensk kärnkraftskapacitet i kombination med en utbyggnad av förnybar elproduktion. För att åstadkomma detta kommer vi att konstruera en allmänjämnviktsmodell med fokus på energimarknaderna. Allmänjämviktsmodellers förmåga att beskriva ekonomiövergripande effekter utgör en viktig skillnad jämfört med andra så kallade partiella modeller. En allmänjämviktsmodell kan fånga upp de återverkningar som sker mellan olika sektorer vid förändringar av ekonomiska förutsättningar och inte bara den direkta påverkan i de berörda sektorerna. Jämfört med partiella modeller fångas de totala samhällsekonomiska konsekvenserna upp på ett mer fullständigt sätt i allmänjämviktsmodeller. Med den typ av allmänjämviktsmodell som vi föreslår, är det möjligt att analysera effekterna av politiska åtgärder riktade till såväl individuella som grupper av kraftkällor i ett systemperspektiv. Verktyget kommer att vara ett viktigt bidrag till förmågan att analysera den svenska energipolitiken i allmänhet och åtgärder som riktar sig utfasning av kärnkraften i synnerhet.
\section{Total project budget}
\section{Research programme (Appendix A)}
\input{inc_appendix_a}
\section{CV (Appendix B)}
\input{inc_appendix_b}
\section{Publication list (Appendix C)}
\input{inc_appendix_c}
\section{Illustrations (Appendix J)}
\input{inc_appendix_j}
\section{Signatures (Appendix S)}



\pagebreak
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{../RefAbstracts}
\bibliographystyle{plainnat}

\end{document}

