\section{Motivation for the Budget Provided}
The project is hosted by the Department of Forest Economics, Swedish University of Agricultural Sciences, Umeå, Sweden. The total cost of the project is estimated at 3 844 kSEK for the project’s 24 months of funding, starting January 1, 2015, and ending December 31, 2016. The group, which will carry out the project, comprises of two post-doctoral researchers.\\*
For more information about the research group and collaboration see project description.\\*\\*
\textbf{Researchers}\\*
Dr. Örjan Furtenback and Dr. Santosh Joshi are post-doctoral members of the research group. Each of them will allocate 100 percent of his working time to the project. They shall participate in the planning and execution of the project, provide advice concerning the research work, including data and methods, and provide constant support and feedback on all aspects of the project, including in preparing the manuscripts for the working paper and scientific journals. Örjan Furtenback will be the principal investigator of the project and as such be responsible for managing and directing the overall project. Örjan Furtenback’s and Santosh Joshi’s salary expenses from the project will amount to 3 434 kSEK in total.\\*\\*
\textbf{Travel costs}\\*
This fund aims mainly at traveling expenses for collaborators Christoph Böhringer, Martin Hill and Badri Narayanan Gopalakrishnan. Uses for research dissemination and presentation of results and methods at national and international workshops and conferences also fall under this account. Cost for data acquisition constitutes the remaining part of the travel fund. In total, the travel cost component adds to 100 kSEK.\\*\\*
\textbf{Premises costs}\\*
The premises costs will amount to 100 kSEK in total.\\*\\*
\textbf{SUMMARY}\\*
\begin{tabular}{ l l c}
  Salaries & 3 434 & kSEK \\
  Office space & 100 & kSEK \\
  Data, travel and other costs & 100 & kSEK \\
  \textbf{Total} & 3 844 & kSEK \\
\end{tabular}


