\textbf{Publication list Santosh Ram Joshi}\\*
\textbf{Peer-reviewed original articles}
\begin{enumerate}
\item Labriet M., Joshi S.R., Babonneau F., Edwards N.R., Holden P.B., Kanudia A.,  Loulou R. and Vielle M. (2013). “Worldwide impacts of climate change on energy for heating and cooling”, Mitigation and Adaptation Strategies for Global Change, DOI 10.1007/s11027-013-9522-7, Published online on 8th November 2013
\item Joshi S.R., Vielle M., Babonneau F., Edwards N.R. and Holden P.B. “Physical and economic consequences of sea-level rise: A coupled GIS and CGE analysis under uncertainties”, on revision in Environmental and Resource Economics.
\end{enumerate}
\textbf{Peer reviewed conference contribution}
\begin{enumerate}
\item Impacts of climate change on heating and cooling: a worldwide estimate from energy and macro-economic perspectives. Presented in Swiss Society of Economics and Statistics (SSES), Neuchatel, Switzerland, June 19$^{th}$ – 21$^{th}$ 2013.
\item Economic consequences of Climate Change, Fifth Integrated Assessment Modeling Consortium (IAMC) Annual Meeting, Utrecht, The Netherlands, 12$^{th}$ – 13$^{th}$ November 2012.
\item Sea level rise and its economic consequences. Presented in International Conference on Economic Modeling (ECOMOD), Seville, Spain, 4$^{th}$ – 6$^{th}$ July 2012.
\item Analyzing the sensitivity of simulated pattern of trade to functional form choices. Presented in International Conference on Economic Modeling (ECOMOD), Istanbul, Turkey,  7$^{th}$ – 10$^{th}$ July 2010.
\item Estimating an Import Demand System using the Generalized Maximum Entropy Method,
European Trade Study Group Conference (ETSG), Lausanne, Switzerland, 9$^{th}$ - 11$^{th}$ September 2010.
\end{enumerate}
